\documentclass[14pt]{exam}

\usepackage{amsmath}
\usepackage{xcolor}

\title{Differential Equations. Week 1}
\date{}

\begin{document}
	\maketitle
	
	\begin{questions}
		
		\question
		(Filipov 79) A large chamber contains 200 cubic meters of gas, 0.15\% of which is carbon dioxide (CO2). A ventilator exchanges 20 cubic meters per minute of this gas with new gas containing only 0.04\% CO2. Write down a differential equation that describes the change of the concentration of CO2.
		 
		\textcolor{cyan}{Answer:} $y' = 0.008 - 0.1y$.
		 
		\question
		(Filipov 83) A raft is being slowed down by resistance of the water, the resistance being proportional to the speed of the raft. Write down a differential equation that describes how the speed of the boat changes in time.
		
		\textcolor{cyan}{Answer:} $v' = -kv$.
		
		\question
		(Filipov 85) It is experimentally determined that every gram of radium loses 0.44 milligrams in 1 year. Write down a differential equation that describes how the mass of the radium changes in time.
		
		\textcolor{cyan}{Answer:} $m' = -km$.
		
		\question
		(Filipov 98) A boat is held by a cable that is wound around a post, the end being held by a laborer. Write down a differential equation that defines how braking force changes with the number of wounds around the post. The coefficient of friction is $\frac{1}{3}$.
		
		\textcolor{cyan}{Answer:} $\frac{dT}{d\theta} = \frac{T}{3}$.
		
		\question
		(Filipov 100) The mass of a rocket, including a full chamber of fuel, is $M$; its net mass (without fuel) is $m$. The products of combustion are ejected with velocity $c$. If the rocket starts from rest, find Ciolkovskii’s formula, which gives the speed imparted to the rocket by the burning of the fuel, neglecting the resistance of the atmosphere.
		
		\textcolor{cyan}{Answer:} $-m \frac{dV}{dt} = c \frac{dm}{dt}$.
	\end{questions}
	
	Use the method of isoclines to solve the differential equation given.
	
	\begin{questions}
		\setcounter{question}{5}
		\question
		(Filipov 6) $xy' = 2y$
		
		\question
		(Filipov 7) $xy' + y = 0$
		
		\question
		(Filipov 16) Give a method for finding the locus of the inflection points of the solutions of the equation.
		
		\begin{parts}
			\part $y' = y - x^2$
			\part $y' = x - e^y$
		\end{parts}
	\end{questions}
	
	Find the differential equations which correspond to the following families of curves.
	
	\begin{questions}
		\setcounter{question}{8}
		\question
		(Filipov 20) $y = \sin(x+ C)$
		
		\question
		(Filipov 25) $y = ax^2 + be^x$
		
		\question
		(Filipov 30) Write the differential equation of circles of radius 1 which have centers on the line $y = 2x$.
		
		\question
		(Filipov 33) Write the differential equation of all parabolas which have axis parallel to the y axis and pass through the origin.
	\end{questions}
	
	Find the differential equations of the trajectories which intersect the given family isogonally at the angle $\phi$:
	
	\begin{questions}
		\setcounter{question}{12}
		\question
		(Filipov 38) $y^2 = x + C$, $\phi=90^\circ$.
		
		\question
		(Filipov 40) $x^2 + y^2 = a^2$, $\phi=45^\circ$.
		
		\question
		(Filipov 42) $3x^2 + y^2 = C$, $\phi=30^\circ$.
	\end{questions}
	
	\textbf{Homework:} Filipov 12, 34, 36, 42.
\end{document}